\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{array}
\usepackage{booktabs}
\usepackage{fontspec}

% Set Times New Roman font
\setmainfont{Times New Roman}

\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE\textbf{Rasila Gautam}} \\[4pt]
    Kathmandu, Nepal \
    \href{mailto:rasilagautam2@gmail.com}{rasilagautam2@gmail.com} $\vert$ +977 9868125455 \
    \href{https://www.linkedin.com/in/rasilagautam123/}{linkedin.com/in/rasilagautam123} $\vert$ 
    \href{https://rasila.com.np/}{rasila.com.np}
\end{center}


Environmental Science graduate with 6+ years of experience in international education consulting, visa documentation, and client counseling. Strong track record in compliance management, stakeholder communication, and project-based volunteering. Detail-oriented and proficient in supporting clients and institutions under strict regulatory frameworks.

\section*{Core Competencies}
\begin{tabular}{@{}ll@{}}
\textbullet~ International Education Consultancy & \textbullet~ Visa Advisory \\
\textbullet~ Client Counseling and Needs Assessment & \textbullet~ Compliance and Regulatory Documentation \\
\textbullet~ Research, Data Analysis, and Reporting & \textbullet~ Report Writing \\
\textbullet~ Stakeholder Communication and Coordination & \textbullet~ Cross-cultural Collaboration \\
\textbullet~ Microsoft Office, Google Suite & \textbullet~ R (Basic), Python (Basic), LaTeX \\
\end{tabular}

\section*{Professional Experience}
\textbf{Pride Abroad Studies Pvt. Ltd.}, Kathmandu, Nepal \
\textit{GTE Officer} \hfill Dec 2020 -- Present
\begin{itemize}[leftmargin=*]
    \item Manage visa processes for Australia, UK, Canada, USA, Ireland, South Korea, etc.
    \item Counsel students aligning academic options with personal goals.
    \item Ensure up-to-date compliance with immigration and institutional rules.
    \item Liaise with universities, embassies, and applicants for smooth application flow.
\end{itemize}

\textbf{Capital International Academy}, Kathmandu, Nepal \
\textit{Counselor \& Documentation Officer} \hfill Jan 2018 -- Dec 2020
\begin{itemize}[leftmargin=*]
    \item Delivered end-to-end application support for UK, Australia, Canada, USA.
    \item Maintained precise documentation and handled day-to-day operations.
    \item Advised applicants on program choices, eligibility, and documentation.
\end{itemize}

\section*{Education}
\begin{tabular}{@{}p{0.7\textwidth}r@{}}
\textbf{MSc Environmental Science}, Tribhuvan University, Kathmandu & 2024 \\
\textbf{BSc Environmental Science}, Tribhuvan University, Nepal & 2018 \\
\end{tabular}

\section*{Certifications \& Trainings}
\begin{itemize}[leftmargin=*]
    \item Leo Leadership Training, Lions Club (Nov 2017)
    \item Community-Based Emergency Response Training, VSO \& Nepal Red Cross (2019)
    \item Concise Vermicomposting Training, NSFT (2016)
    \item Fundraising: "The Great Centurian", Community School Initiative (2016)
\end{itemize}

\section*{Technical Skills}
\begin{tabular}{@{}ll@{}}
\textbf{Office Tools:} & Microsoft Office, Google Suite \\
\textbf{Communication:} & Fluent in English and Nepali; Conversational Hindi \\
\textbf{Research:} & Literature review, survey design, data analysis, report writing \\
\textbf{Programming:} & R (Basic), Python (Basic), LaTeX \\
\end{tabular}

\section*{Research and Publications}
\begin{itemize}[leftmargin=*]
    \item \textbf{Research Paper:} Impact of Climate Variability on Agricultural Productivity and Food Security in Banke, Nepal (1990–2020). DOI: \href{https://doi.org/10.61440/JESAR.2025.v3.51}{doi.org/10.61440/JESAR.2025.v3.51}
    \item \textbf{Master's Thesis:} Climatic Variables and Crop Production in Janaki RM, Banke
    \item \textbf{Bachelor's Thesis:} Water Quality Assessment of Bagmati River Using CWQI
\end{itemize}

\section*{Volunteering and Leadership}
\begin{itemize}[leftmargin=*]
    \item \textbf{VSO/ICS Volunteer}, Lalitpur (Jul--Oct 2018): Projects on gender inclusion and disaster risk governance in Changunarayan-8, Bhaktapur.
    \item \textbf{Leo Clubs:}
    \begin{itemize}
        \item Member, Leo Club of Kathmandu Sauharda (2021--Present)
        \item Board Member, Kathmandu Sauharda (2020--2021); Kathmandu Dreams (2017--2020)
    \end{itemize}
    \item Led programs in heritage cleaning, event hosting, disaster response, and community training.
\end{itemize}

\section*{Languages}
\begin{tabular}{@{}ll@{}}
Nepali: & Native \\
English: & Fluent (IELTS 7.5, no band below 7) \\
Hindi: & Conversational \\
\end{tabular}

\section*{References}
\textbf{Ms. Mala Pradhan} \\
Project Coordinator, VSO Placement Changunarayan \\
\href{mailto:mala.pradhan92@gmail.com}{mala.pradhan92@gmail.com} \\
\textit{Education Agent References available upon request}




\end{document}
