\documentclass[a4paper, 09pt]{extarticle}
\usepackage[utf8]{inputenc} 
\usepackage{geometry} 
\geometry{letterpaper, margin=0.2in} 
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} 
\usepackage{hyperref} 
\usepackage{tabularx}
\usepackage{fancyhdr}

\setlist{noitemsep} 
\titleformat{\section}{\large\bfseries}{\thesection}{2em}{}[\titlerule] 
\titlespacing*{\section}{1pt}{\baselineskip}{\baselineskip}
\begin{document}



\begin{center}
\textbf{\huge Bishwa Prakash Puri}\\[4pt] 
Assistant Lecturer, College of Applied Sciences-Nepal, Kathmandu, Nepal\\
\href{mailto:mabishwapuri@gmail.com}{mabishwapuri@gmail.com}, 
\href{tel:+9779843314630}{+977 9843314630} \\
\href{https://workbishwa.github.io/imBishwa/}{workbishwa.github.io/imBishwa/}

\end{center}

Growing up in Nepal's Koshi Basin, I developed a deep commitment to understanding and addressing environmental challenges in Himalayan communities. My expertise spans climate data analysis, multi-hazard risk assessment, and hydrological modeling, supported by strong programming skills in Python, R, and GIS technologies. As an environmental consultant and assistant lecturer in Environmental Modeling, I combine technical proficiency with practical field experience to develop solutions for disaster risk reduction and sustainable development. My research on temperature trends and agricultural impacts in the Koshi Basin, along with my experience in environmental impact assessments, has equipped me to bridge scientific modeling with community-focused solutions.

\section*{EDUCATION}

\textbf{Tribhuvan University (MSc.)} \hfill \textbf{2024}\\[2pt] 
College of Applied Sciences-Nepal, Kathmandu, Nepal\\
Master of Science in Environmental Science

\vspace{5pt}

\noindent
\textbf{Tribhuvan University (BSc.)} \hfill \textbf{2019}\\[2pt] 
Tri-Chandra Multiple Campus, Kathmandu, Nepal\\
Bachelor of Science in Environmental Science

\vspace{5pt}

\section*{ACADEMIC EXPERIENCE}
\noindent
\textbf{College of Applied Sciences-Nepal} \hfill Kathmandu, Nepal\\[2pt] 
\textit{Assistant Lecturer} \hfill November 2024--January 2025 
\begin{itemize}
    \item Teaching Environmental Modeling to MSc 4th-semester students, focusing on hydrological modeling (HEC-HMS, HEC-RAS), climate modeling (SDSM), and geospatial analysis (GIS).
    \item Designing and delivering lectures, leading hands-on practical sessions, and mentoring students in applying modeling tools to environmental challenges.
    \item Serving as a thesis co-supervisor, guiding research projects and ensuring academic and professional excellence.
\end{itemize}

\vspace{5pt}

\section*{PROFESSIONAL EXPERIENCE}
\noindent
\textbf{Freelancer} \hfill Nepal\\[2pt] 
\textit{Environmental Consultant, Researcher, Business Development Consultant} \hfill  August 2024--Present
\begin{itemize}
    \item Preparation of EIA, IEE, and Monitoring Reports for hydropower projects.
    \item Conduct fieldwork and assess environmental impacts of hydroelectric projects.
    \item Consultations with stakeholders.
    \item Preparation and presentations of reports.
    \item Business development and growth strategies for small businesses consultancy firms.
\end{itemize}

\noindent
\textbf{Quest Forum, SMS Environment and Engineering Pvt. Ltd.} \hfill Kathmandu, Nepal\\[2pt] 
\textit{Environmental Assistant} \hfill January 2023--June 2023
\begin{itemize}
    \item Assisted in environmental studuies including preparation of reports, preparation of Terms of References (TOR), faciliation of public hearing, data collection, preparation of presentations.
    \item Compilation of technical and financial documents for Biding.
    \item Assisted in field visits for environmental monitoring in various industries from different sectors such as Brick, Cement, Beverage, and Pharmaceuticals.
    \item Assisted in Ppreparation of Environmental Monitoring Report.
    \item Communicated findings and recommendations to clients, stakeholders, and regulatory bodies.
\end{itemize}

\noindent
\textbf{Nepal Environmental and Scientific Services (NESS)} \hfill Kathmandu, Nepal\\[2pt] 
\textit{MSDS Officer Intern} \hfill July 2022 -- December 2022
\begin{itemize}
    \item Prepared laboratory consumables inventory and created material safety data sheets (MSDS).
\end{itemize}

\section*{PUBLICATIONS}
\noindent
\textbf{Journal Articles}
\begin{itemize}
    \item Puri, B. P., Adhikari, T. R., et al. \href{https://doi.org/10.3126/jhm.v12i1.72654}{\textit{Spatial and Temporal Variations of Surface Air Temperature (1962–2022) across Physiographic Regions in the Koshi Basin, Nepal.}} Published in \href{https://soham.org.np/}{\textit{SOHAM.}}
    \item Gautam, R., Puri, B. P, et al. \href{https://oaskpublishers.com/assets/article-pdf/impact-of-climate-variability-on-agricultural-productivity-and-food-security--in-banke-nepal-insights-from-1990-2020.pdf}{\textit{Impact of Climate Variability on Agricultural Productivity and Food Security in Banke, Nepal: Insights from 1990--2020}}. Published in \href{https://oaskpublishers.com/}{\textit{OASK Publishers.}}
    \item Research Paper (In Progress): \textit{Assessing Soil Nutrient Dynamics and Their Impacts on Crop Yields: A Case Study of Janaki Rural Municipality, Banke, Nepal}. 
\end{itemize}

\noindent
\textbf{Thesis}
\begin{itemize}
    \item Temperature Trend Analysis Along with Paddy Production Trend and Their Impact on Paddy Cultivation in Koshi Basin, Nepal.

\end{itemize}

\section*{RESEARCH AND FIELD EXPERIENCE}
\begin{itemize}
    \item Conducted flood frequency analysis using Gumbel’s Distribution Method and HEC-HMS, and developed river channel geometry for Balkhu River Basin using HEC-RAS.
    \item Simulated rainfall data using Statistical Downscaling Modelling (SDSM) during the Flood and Hydrological Modeling Project in Surkhet Weather Station, Nepal.
    \item Conducted geological data collection, input, and analysis in Kakani Ranipauwa Area, Nuwakot District, Nepal.
    \item Geological and Ecological Field Study, Malekhu – Pokhara, Nepal: Conducted geo-environmental studies on rock mass classification, slope stability, landslides, and biodiversity; created environmental geological maps and assessed fluvial deposits.
    \item Led community-based solid waste segregation initiatives at Sunrise English Boarding School, Sainbu, Lalitpur, Nepal, including managing solid waste and conducting field-based data collection.
    \item Emission inventory from cement production in Nepal:  Annual pollutant emission that generate from the Shivam and Hongshi cement industries was calculated and estimated by the help of default emission factor for different pollutant.
    \item Emission inventory from hospital: Conducted an emission inventory analysis of NOx, CO, and SOx from Bir Hospital and Grande Hospital, including calculations of mercury and lead emissions during clinical waste incineration.
    \item Water quality monitoring of ground water and irrigation water: Conducted water quality monitoring of surface and groundwater of Koplu Khola, Nuwakot, analyzing parameters such as temperature, pH, EC, TDS, TSS, heavy metals, and coliform bacteria.
    \item Measurement and comparison of noise level (equivalent, percentile) in residential, public and workplaces: Compared and identified the noise level within Balkhu and nearby areas.
\end{itemize}

\vspace{5pt}



\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming:} Python, R
    \item \textbf{Software:} ArcGIS, HEC-HMS, HEC-RAS, SDSM, LaTeX, Markdown, Git
    \item \textbf{Technical:} Field Surveys, EIA/IEE/BES, Report Writing, Stakeholder Consultations
\end{itemize}

\section*{TRAINING AND CERTIFICATIONS}
\begin{itemize}
    \item Geographic Information System (GIS) Certification – 1 Month (2020)
    \item Chemical Management and MSDS Certification – 2 Weeks (2022)
    \item Electricity Grid Modernization Project (EGMP) NEA-Environment and social safeguards training – 1 Week (2024)
    
\end{itemize}

\section*{Language Skills}

\noindent
\begin{tabularx}{\textwidth}{|l|X|X|X|}
\hline
\textbf{Language} & \textbf{Reading} & \textbf{Writing} & \textbf{Speaking} \\ \hline
Nepali & Native & Native & Native \\ \hline
English & Excellent & Excellent & Good \\ \hline
Hindi & Excellent & Beginners & Intermediate \\ \hline
\end{tabularx}

\section*{REFERENCES}

\noindent
\textbf{Dr. Bhupendra Devkota}\\[2pt]
\textit{Principal, Professor, College of Applied Sciences-Nepal}\\
\href{mailto:bhupendra.devkota@gmail.com}{bhupendra.devkota@gmail.com}

\vspace{10pt}

\noindent
\textbf{Dr. Tirtha Raj Adhikari}\\[2pt]
\textit{Professor Emeritus, Tribhuvan University}\\
\href{mailto:tirtha43@gmail.com}{tirtha43@gmail.com}

\vspace{5pt}

\noindent
\textbf{Surendra Dev Bhatta}\\[2pt]
\textit{Executive Director, Green Globe International Pvt. Ltd.}\\
\href{mailto:surenbtta@gmail.com}{surenbtta@gmail.com}

\section*{Consultations and Projects Direcories for References}
\begin{itemize}
    \item EIA, IEE, Reports preparation and Field Visits.
    \begin{itemize}
        \item Lower Arun Power Development  (335MW), Sankhuwasabha
        \item Karuwa Seti Hydropower Project (SEIA, 32 MW), Pokhara Kaski
        \item Kanke-Deurali Dam Project, Department of Water and Sewerage management, Madane Rural Municipality, Gulmi
        \item Myagdi Khola Hydropower (65MW), Myagdi
        \item Molung Khola Hydropower (8.53MW), Okhaldhunga
        \item Lapa Khola Hydropower (4.99MW), Dhading
        \item Chaurjahari Hospital,  Rukum
        \item Om Foods Pvt. Ltd., Kailali
        \item Hulas Steel Industries Pvt. Ltd.,  Birgunj, Parsa
        \item Aanandam Snacks and Beverages Pvt. Ltd. Birgunj, Parsa
        \item Planet Green Recycling Pvt. Ltd. Dhanusa
        \item Kalpa Metals Pvt. Ltd.,  Bara 
        \item Dugar Spices and Food Products Pvt. Ltd. Morong
        \item Kantipur Washing Udhyog Pvt. Ltd. Morong
        \item Lumbini Gas Company Pvt. Ltd. Rupandehi
        \item Nava Prabhat Dairy Pvt. Ltd. Lalitpur
        \item Reliance Spinning Mills Limited, Sunsari
        \item Laxmi Motor Corporation Pvt. Ltd. Nawalparasi (Bardaghat Susta West)
        \item Janakpur Refineries Pvt. Ltd. Dhanusa
        \item United Pharmaceuticals Industries Pvt. Ltd. Jhapa
        \item Many More ...

    \end{itemize}
    \item Environmental Monitoring
    \begin{itemize}
        \item Panchakanya Steel, Panchakanya Group,Tilottama-15, Rupandehi,
        \item Kathmandu Steel Pvt. Ltd. Sarawal Rural Municipality-1, Nawalparasi (Bardaghat Susta West),
        \item Upahar Feeds Pvt. Ltd. Ramdhuni-14, Sunsari
        \item Progeochem Industries Pvt. Ltd. Parwanipur Rural Municipality-05, Bara
        \item Probiotech Industries Ltd. Birgunj Metropolitancity-21, Parsa
        \item Progeochem Industries Pvt. Ltd. HID, Hetauda, Makawanpur
        \item Himalayan Distillery Limited. Birgunj -21, Parsa
        \item Asian Biscuit and Confectionery Pvt. Ltd. Duhabi, Sunsari
        \item Maruti Cements Ltd. (MCL) Golbazar-9, Siraha
        \item Shivam Cement Ltd. Hetauda-16, Makawanpur
        \item Ambe Steels Pvt. Ltd. Mayadevi Gaupalika-6, Rupandehi, Nepal
        \item QBD Pharmaceuticals Pvt. Ltd. Sanga, Banepa -14, Kavre
        \item Vijaya Distillery Pvt. Ltd., Raj Brewery Pvt. Ltd., Rolling River Distilleries Pvt. Ltd. by Jawalakhel Group of Industries
        \item Agromix feed Industries Pvt.Ltd. Ratnanagar Municipality, Chitwan
        \item Hulas Steel Industries Ltd. (Unit 1) Jeetpur Simara Sub-metropolitan City-02, Bara
        \item Nuplast Industries Pvt. Ltd. Jeetpur Simara Sub-metropolitian, Bara
        \item Jagdamba Enterprises Pvt. Ltd. Birgunj Metropolitan city-32, Parsa
        \item Ganapati Vanaspati Pvt. Ltd. Jeetpur Simara Sub-metropolitan City, Bara
        \item RMC Cement Pvt. Ltd. Jeetpur Simara Sub-metropolitan City, Bara
        \item Rajesh Metals and Crafts Pvt. Ltd. Jeetpur Simara Sub-metropolitan City, Bara
        \item Jagdamba Enterprises Pvt. Ltd., Birgunj-32, Parsa
        \item RMC Foods Pvt. Ltd. Jeetpur Simara Sub-metropolitan City, Bara
        \item Brick Factories (Brahmayani Mahadevi Fix Itta Udhyog, Hanuman Bricks, Maitri Hanuman Bricks, Changu narayan Itta Udhyog, Barahi Brick Factory, \dots)
        \item Many More ...
    \end{itemize}
    \item  Central Treatment Facility project for Kathmandu valley (Research Projects),  \item International Labour Organization (ILO) projects on occupational safety and health (OSH) for tea laborers (Research Projects)



\end{itemize}

\end{document}
