\documentclass[11pt]{letter}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{lmodern}

\begin{document}

\begin{letter}{To the Selection Committee\\
International Centre for Integrated Mountain Development (ICIMOD)\\}

\opening{Dear Selection Committee,}

\onehalfspacing

\textbf{Subject: Application for YIPP 2025/26 – Interest in Cryosphere and Water/Living Mountain Lab/Landscapes/ or Regional Action}

I am writing to express my strong interest in the Young ICIMOD Professionals Programme (YIPP) 2025/26, with particular focus on the action areas of \textbf{Cryosphere and Water}, \textbf{Living Mountain Lab}, \textbf{Landscapes}, and \textbf{Regional Action}. With a Master’s degree in Environment and a diverse portfolio of research, consultancy, and academic engagement, I am motivated to contribute meaningfully to ICIMOD’s mission of fostering sustainable, climate-resilient development across the Hindu Kush Himalaya (HKH) region.

My academic foundation is rooted in environmental science and policy. Under the mentorship of Prof. Emeritus Tirtha Raj Adhikari, I completed a research-based Master’s degree that deepened my understanding of ecological systems, climate impacts, and sustainable planning. As a \textit{freelance environmental consultant}, I have worked extensively on the development of Terms of Reference (ToRs), preparation of Initial Environmental Examinations (IEE) and Environmental Impact Assessments (EIA), and facilitation of \textit{community consultations}—particularly within hydropower and infrastructure projects in Nepal. These experiences have equipped me with both technical writing skills and field-level insights into the region’s environmental and socio-economic complexities.

Parallel to my consultancy work, I serve as a \textit{business development consultant}, where I perform market analyses, develop marketing strategies, and conduct cost-benefit assessments for enterprises seeking growth within sustainable parameters. This dual role has helped me understand the link between ecological integrity and economic resilience—an essential aspect of ICIMOD’s integrated approach to mountain development.

My teaching and thesis co-supervision roles at the \textit{College of Applied Sciences} have also strengthened my academic engagement and mentoring skills. I have guided students working on climate change, water resource management, and community-based conservation, aligning closely with ICIMOD’s core areas such as \textbf{Cryosphere and Water} and \textbf{Living Mountain Lab}.

I am particularly drawn to the following YIPP action areas:

\begin{itemize}
  \item \textbf{Cryosphere and Water}: Given my background in hydropower and interest in water resource governance, I am keen to support research and action on glacial melt, cryosphere monitoring, and transboundary water cooperation.
  
  \item \textbf{Living Mountain Lab}: My work with communities and local governments positions me well to contribute to field-based pilot projects that bridge science and community-led innovation.
  
  \item \textbf{Landscapes}: I am enthusiastic about contributing to integrated landscape management approaches, particularly those that balance biodiversity conservation with sustainable livelihoods.
  
  \item \textbf{Regional Action}: As someone deeply engaged in stakeholder consultations and inter-agency coordination, I am excited by the opportunity to facilitate knowledge sharing and policy dialogue across the HKH.
\end{itemize}

Joining YIPP represents a unique opportunity for me to expand my capabilities through interdisciplinary learning, cross-cultural collaboration, and practical problem-solving. I am confident that my skills in environmental assessment, policy engagement, communication, and local-level facilitation will allow me to make a valuable contribution to ICIMOD’s Strategy 2030 and its Medium-Term Action Plan.

Thank you for considering my application. I would be honored to bring my experience, motivation, and regional understanding to the dynamic ICIMOD community.

\closing{Sincerely,}

\vspace{1em}
\noindent
\textbf{Bishwa Prakash Puri} \\
Environmental \& Business Development Consultant \\
\texttt{mabishwapuri@gmail.com} \\
\texttt{+977-9843314630} \\
Kathmandu, Nepal

\end{letter}

\end{document}
