\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{setspace}

\begin{document}

\begin{center}
    {\LARGE \textbf{Rasila Gautam}} \\
    Kathmandu, Nepal \\
    Phone: +977 9868125455 \\
    Email: \href{mailto:rasilagautam2@gmail.com}{rasilagautam2@gmail.com} \\
    LinkedIn: \href{https://linkedin.com/in/rasilagautam123}{linkedin.com/in/rasilagautam123}
\end{center}

\vspace{0.3cm}

\section*{Personal Statement}
A dedicated and highly motivated Environmental Science graduate with over five years of academic and research experience focused on climate change, hydrological modeling, and environmental sustainability. I have a strong track record in field-based research and data analysis, demonstrated through various high-altitude field studies and a Master's thesis on climate impacts in the Koshi Basin. With proven expertise in research design, fieldwork, and technical report writing, I am eager to contribute to understanding the water cycle and precipitation patterns in mountainous regions. My strengths lie in interdisciplinary collaboration, problem-solving, and innovative thinking, making me a strong candidate for a PhD position in climate science.

\vspace{0.3cm}

\section*{Education}
\noindent
\textbf{Master of Science in Environmental Science} \\
College of Applied Sciences, Tribhuvan University, Nepal \\
Graduation: 2024 \\
\textit{Thesis}: "Impact of Climatic Variables on Crop Production and the Role of Environmental Factors in Janaki Rural Municipality, Banke, Nepal" \\
Relevant coursework: Climate and Hydrological Modeling, GIS, Atmospheric Science

\vspace{0.2cm}

\noindent
\textbf{Bachelor of Science in Environmental Science} \\
Trichandra Multiple Campus, Tribhuvan University, Nepal \\
Graduation: 2018 \\
\textit{Thesis}: "Assessment of Water Quality of Bagmati River by the Application of Canadian Water Quality Index along Kathmandu Valley" \\
Relevant coursework: Environmental Impact Assessment, Field Methods in Environmental Science

\vspace{0.3cm}

\section*{Research and Field Experience}
\noindent
\textbf{Flood and Hydrological Modeling Project} \\
Kathmandu, Nepal \\
2024 \\
\begin{itemize}[noitemsep]
    \item Conducted flood frequency analysis using Gumbel’s Distribution Method and HEC-HMS.
    \item Developed river channel geometry for Balkhu River Basin using HEC-RAS.
    \item Simulated rainfall data using Statistical Downscaling Modelling (SDSM).
\end{itemize}

\vspace{0.2cm}

\noindent
\textbf{Geological and Ecological Field Study} \\
Malekhu – Pokhara, Nepal \\
2023 \\
\begin{itemize}[noitemsep]
    \item Conducted geo-environmental study focusing on rock mass classification and slope stability.
    \item Performed biodiversity assessments and analyzed fluvial deposits.
\end{itemize}

\vspace{0.2cm}

\noindent
\textbf{Environmental Geological Field Study} \\
Kakani Ranipauwa, Nuwakot District, Nepal \\
2022 \\
\begin{itemize}[noitemsep]
    \item Assessed ambient air quality in the Kathmandu Valley.
    \item Performed geological data collection and interpretation.
\end{itemize}

\vspace{0.2cm}

\noindent
\textbf{Community-Based Solid Waste Management \& Disaster Risk Management} \\
Budhanilkantha Municipality, Kathmandu, Nepal \\
2023 \\
\begin{itemize}[noitemsep]
    \item Led disaster risk management and solid waste management initiatives.
    \item Organized field-based data collection and community engagement activities.
\end{itemize}

\vspace{0.3cm}

\section*{Technical Skills}
\begin{itemize}[noitemsep]
    \item \textbf{Programming Languages}: Python (Basic), R (Intermediate)
    \item \textbf{Software}: GIS, SPSS, HEC-RAS, HEC-HMS
    \item \textbf{Data Analysis}: Field-based research, climate and hydrological modeling
    \item \textbf{Remote Sensing}: Analysis of large-scale datasets and atmospheric models
    \item \textbf{Languages}: Nepali (native), English (fluent), Hindi (conversational)
\end{itemize}

\vspace{0.3cm}

\section*{Professional Experience}
\noindent
\textbf{GTE Officer / Documentation Officer} \\
PRIDE ABROAD STUDIES PVT. LTD., Kathmandu, Nepal \\
2020 – Present \\
\begin{itemize}[noitemsep]
    \item Assisted in visa documentation and study abroad counseling for students applying to universities in Canada, Australia, USA, and European countries.
    \item Managed application processes and guided applicants through research and submission phases.
\end{itemize}

\vspace{0.2cm}

\noindent
\textbf{Action Learner} \\
Volunteer Service Overseas (VSO) / International Citizen Service \\
2018 \\
\begin{itemize}[noitemsep]
    \item Facilitated disaster risk reduction training and led awareness sessions on inclusive education in schools and communities.
    \item Coordinated disaster preparedness programs and community outreach.
\end{itemize}

\vspace{0.3cm}

\section*{Training and Certifications}
\begin{itemize}[noitemsep]
    \item \textbf{Geographic Information System (GIS)}: 1-month certification (2020)
    \item \textbf{Environmental Impact Assessment (EIA)}: 3-week certification (2020)
    \item \textbf{Community-Based Emergency Response Training}: Nepal Red Cross Society collaboration (2019)
    \item \textbf{Chemical Management \& MSDS}: 2-week certification (2022)
\end{itemize}

\vspace{0.3cm}

\section*{Leadership and Community Involvement}
\noindent
\textbf{Board Member / General Member} \\
Leo Club of Kathmandu Sauharda \\
2021 – Present \\
\begin{itemize}[noitemsep]
    \item Led several heritage cleaning initiatives and disaster response efforts.
    \item Volunteered in community engagement and fundraising activities.
\end{itemize}

\vspace{0.3cm}

\section*{References}
\noindent
\textbf{Bhupendra Devkota, PhD} \\
Principal, College of Applied Sciences-Nepal \\
Email: \href{mailto:bhupendra.devkota@gmail.com}{bhupendra.devkota@gmail.com}

\vspace{0.2cm}

\noindent
\textbf{Dr. Hari Dahal} \\
Professor of Agriculture and Research Methodology \\
Email: \href{mailto:dahaldr.hari@gmail.com}{dahaldr.hari@gmail.com}

\vspace{0.2cm}

\noindent
\textbf{Dr. Tirtha Raj Adhikari} \\
Professor of Meteorology and Hydrology \\
Email: \href{mailto:tirtha43@gmail.com}{tirtha43@gmail.com}

\vspace{0.2cm}

\noindent
\textbf{Ms. Mala Pradhan} \\
Project Coordinator, Volunteer Service Overseas \\
Contact: Available upon request

\end{document}
