\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=0.75in}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{setspace}

% Reduce space between section title and content
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.5\baselineskip}

% Reduce item spacing
\setlist{itemsep=1pt,topsep=1pt,leftmargin=*}

\begin{document}

% Name and contact details
\begin{center}
    {\LARGE \textbf{Rasila Gautam}} \\
    Kathmandu, Nepal | Phone: +977 9868125455 \\
    Email: \href{mailto:rasilagautam2@gmail.com}{rasilagautam2@gmail.com} | LinkedIn: \href{https://linkedin.com/in/rasilagautam123}{linkedin.com/in/rasilagautam123}
\end{center}

\vspace{0.2cm}

% Personal Statement
\section*{Personal Statement}
A dedicated Environmental Science graduate with five years of academic and research experience in climate change, hydrological modeling, and environmental sustainability. Experienced in high-altitude field studies, data analysis, and climate impact assessments, I am eager to contribute to research on water cycles and precipitation patterns in mountainous regions. Strengths include interdisciplinary collaboration, problem-solving, and innovative thinking.

\vspace{0.2cm}

% Education Section with two columns
\section*{Education}
\begin{multicols}{2}

% First column
\noindent
\textbf{M.Sc. in Environmental Science} \\
College of Applied Sciences, Tribhuvan University \\
Graduation: 2024 \\
\textit{Thesis}: "Impact of Climatic Variables on Crop Production in Janaki Rural Municipality, Banke, Nepal" \\
Relevant coursework: Climate Modeling, GIS, Atmospheric Science

\vspace{0.2cm}

% Second column
\noindent
\textbf{B.Sc. in Environmental Science} \\
Trichandra Multiple Campus, Tribhuvan University \\
Graduation: 2018 \\
\textit{Thesis}: "Water Quality Assessment of Bagmati River in Kathmandu" \\
Relevant coursework: EIA, Field Methods in Environmental Science

\vspace{0.2cm}

\end{multicols}

% Research and Field Experience
\section*{Research and Field Experience}

\begin{multicols}{2}

% First column
\noindent
\textbf{Flood and Hydrological Modeling Project} \\
Kathmandu, Nepal \\
2024 \\
\begin{itemize}
    \item Conducted flood frequency analysis using Gumbel’s Method and HEC-HMS.
    \item Developed river channel geometry using HEC-RAS.
    \item Simulated rainfall data using Statistical Downscaling Modelling (SDSM).
\end{itemize}
\vspace{0.1cm}
\noindent
\textbf{Environmental Geological Study} \\
Kakani Ranipauwa, Nuwakot, Nepal \\
2022 \\
\begin{itemize}
    \item Assessed ambient air quality and geological data collection.
\end{itemize}

% Second column
\noindent
\textbf{Geological \& Ecological Field Study} \\
Malekhu – Pokhara, Nepal \\
2023 \\
\begin{itemize}
    \item Conducted geo-environmental study on rock mass classification and slope stability.
    \item Performed biodiversity assessments and fluvial deposit analysis.
\end{itemize}

\noindent
\textbf{Community-Based Disaster Risk Management} \\
Budhanilkantha Municipality, Nepal \\
2023 \\
\begin{itemize}
    \item Led disaster risk management and solid waste management initiatives.
    \item Organized community engagement and field-based data collection.
\end{itemize}

\end{multicols}

\vspace{0.2cm}

% Technical Skills
\section*{Technical Skills}
\begin{itemize}
    \item \textbf{Programming}: Python (Basic), R (Intermediate)
    \item \textbf{Software}: GIS, SPSS, HEC-RAS, HEC-HMS
    \item \textbf{Data Analysis}: Climate and hydrological modeling, large-scale datasets
    \item \textbf{Languages}: Nepali (native), English (fluent), Hindi (conversational)
\end{itemize}

\vspace{0.2cm}

% Professional Experience
\section*{Professional Experience}
\noindent
\textbf{GTE Officer / Documentation Officer} \\
PRIDE ABROAD STUDIES PVT. LTD., Kathmandu, Nepal \\
2020 – Present \\
\begin{itemize}
    \item Managed visa documentation for students applying to universities abroad.
    \item Guided applicants through research, submission, and application processes.
\end{itemize}

\noindent
\textbf{Action Learner} \\
Volunteer Service Overseas (VSO) / International Citizen Service \\
2018 \\
\begin{itemize}
    \item Facilitated disaster risk reduction training and led awareness sessions.
    \item Coordinated community disaster preparedness programs.
\end{itemize}

\vspace{0.2cm}

% Training and Certifications
\section*{Training and Certifications}
\begin{itemize}
    \item \textbf{GIS}: 1-month certification (2020)
    \item \textbf{Environmental Impact Assessment (EIA)}: 3-week certification (2020)
    \item \textbf{Community-Based Emergency Response Training}: Nepal Red Cross Society (2019)
\end{itemize}

\vspace{0.2cm}

% Leadership and Community Involvement
\section*{Leadership and Community Involvement}
\noindent
\textbf{Board Member / General Member} \\
Leo Club of Kathmandu Sauharda \\
2021 – Present \\
\begin{itemize}
    \item Led heritage cleaning initiatives and disaster response efforts.
    \item Organized community engagement and fundraising activities.
\end{itemize}

\vspace{0.2cm}

% References
\section*{References}
\noindent
\textbf{Bhupendra Devkota, PhD} \\
Principal, College of Applied Sciences, Nepal \\
Email: \href{mailto:bhupendra.devkota@gmail.com}{bhupendra.devkota@gmail.com}

\vspace{0.2cm}

\noindent
\textbf{Dr. Hari Dahal} \\
Professor of Agriculture and Research Methodology \\
Email: \href{mailto:dahaldr.hari@gmail.com}{dahaldr.hari@gmail.com}

\vspace{0.2cm}

\noindent
\textbf{Dr. Tirtha Raj Adhikari} \\
Professor of Meteorology and Hydrology \\
Email: \href{mailto:tirtha43@gmail.com}{tirtha43@gmail.com}

\end{document}
