\documentclass[a4paper,12pt]{letter}
\usepackage{mathptmx}
\usepackage{geometry}
\geometry{left=0.81in, right=0.41in, top=0.41in, bottom=0.41in}
\address{Kapan\\Kathmandu, Bagmati\\mabishwapuri@gmail.com\\9843314630}
\date{\today}

\begin{document}

\begin{letter}{Hiring Manager\\Red Cross Red Crescent Climate Centre\\Anna van Saksenlaan 50, 2593 HT, The Hague, Netherlands}

\opening{Dear Hiring Manager,}

I am excited to apply for the Intern – Climate Programming and Nature-based Solutions position with the Red Cross Red Crescent Climate Centre. With a Master’s degree in Environmental Science and hands-on experience in community engagement, report writing, and environmental consultancy, I am eager to contribute to the Climate Smart Livelihood Programming and Nature-based Solutions project in Nepal.

My keen interest in climate change is reflected in my thesis on temperature trend analysis in the Koshi Basin, which is soon to be published. This work has deepened my understanding of climate change. I am eager to further explore risks and vulnerabilities associated with it, and to understand locally implemented strategies and measures designed to build resilience, known as "climate-smart" solutions. The chance to work on this project excites me because it offers a comprehensive learning experience, including opportunities to deepen my knowledge of climate risks, enhance my practical research and fieldwork skills, and collaborate with experienced professionals.

I am confident in my ability to fulfill the responsibilities of this role effectively. My experience includes conducting community vulnerability assessments, reporting on human-wildlife conflicts, and performing environmental impact assessments (IEE/EIA). These experiences have equipped me with strong skills in field surveys, community and stakeholder engagement, and developing detailed reports. I am well-prepared for responsibilities with projects, including conducting key informant interviews and consultations.

My hands-on experience with fieldwork and community consultations, coupled with excellent communication skills and the ability to work independently, positions me well for the tasks involved. I am familiar with socio-economic contexts and climate resilience strategies, which will aid in mapping key NbS interventions and developing impactful case studies and advocacy materials. In addition, my background in reviewing and enhancing documentation, including research papers and monitoring reports, will help me contribute effectively to creating publishable briefs and visuals. My technical skills in data compilation, analysis, and methodological adaptation will support the refinement of the EVCA tools and their documentation. Moreover, my ability to coordinate with various stakeholders and work within intercultural teams will facilitate smooth collaboration with NRCS, BRC Nepal, and other partners. I am also prepared to conduct remote consultations with BRC Bangladesh and support the team as needed.

Overall, my work ethic, dedication, and blend of technical expertise, research skills, and commitment to climate-smart solutions align with the responsibilities of this role. I am enthusiastic about contributing to the Climate Centre's mission and would appreciate the opportunity to discuss how my background aligns with the needs of your team.

Thank you for considering my application. I look forward to the possibility of contributing to your impactful work.

\vspace{1.3em}

Sincerly,\\
Bishwa Prakash Puri


\end{letter}

\end{document}
