\documentclass[a4paper,12pt]{article}
\usepackage{adjustbox}
\usepackage{authblk}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{booktabs}
\usepackage[utf8]{inputenc}

\usepackage[numbers]{natbib}
\bibliographystyle{unsrtnat} 

\usepackage{caption}

\usepackage{hyperref} 
\usepackage{setspace}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{tabularx}



\usepackage{float}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{titlesec}
\titleformat{\section}{\normalfont\Large\bfseries}{\thesection}{1em}{\MakeUppercase}



% Title and author information
\title{Impact of Climate Variability on Agricultural Productivity and Food Security in Banke, Nepal: Insights from 1990--2020}

\author[1]{Rasila Gautam}

\author[1]{Bishwa Prakash Puri}
\author[2,3]{Madan Sigdel*}
\author[1]{Hari Dahal}

\affil[1]{College of Applied Sciences-Nepal, Tribhuvan University, Kathmandu, Nepal}
\affil[2]{CAS-TU, Central Department of Hydrology and Meteorology, Tribhuvan University}
\affil[3]{Kathmandu Centre for Research and Education (KCRE)}
\affil[*]{Correspondence Author: \texttt{madan.sigdel@cdhm.tu.edu.np}}

\date{}  


\begin{document}
\maketitle

\section*{Abstract}
\input{sections/abstract}


\section{Introduction}
\input{sections/introduction}

\section{Study area, and Methodology}
\input{sections/materials_method}

\section{Results and Discussion}
\input{sections/results_discussion}



\section{Conclusion}
\input{sections/conclusion}

\section*{Author Contribution}
\begin{itemize}
    \item \textbf{Rasila Gautam}: Conceptualization, Methodology, Data collection, Analysis, Writing - Original Draft.
    \item \textbf{Bishwa Prakash Puri}: Data Analysis, Writing - Review \& Editing.
    \item \textbf{Madan Sigdel}: Review \& Publication.
    \item \textbf{Hari Dahal}: Supervision, Methodology, Project Administration.
\end{itemize}
\section*{Funding}
This research was part of master's thesis work of first author Rasila Gautam.


\section*{Acknowledgments}
The authors express their gratitude to the College of Applied Sciences-Nepal, Tribhuvan University, Kathmandu, Nepal, for their support in conducting this research. We also extend our thanks to Dr. Bhupendra Devkota and Dr. Tirtha Raj Adhikari for their insightful and valuable suggestions.


\section*{Conflicts of Interest}
The authors declare no conflicts of interest.


\bibliography{reference_cc_bibtex}

\end{document}
