\documentclass[12pt]{letter}

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\signature{Dr. Hari Dahal \\ Associate Professor \\ College of Applied Sciences-Nepal, Tribhuvan University}
\address{College of Applied Sciences-Nepal \\ Tribhuvan University \\ Kathmandu, Nepal \\ hari.dahal@coas.tu.edu.np}

\begin{document}

\begin{letter}{Admissions Committee}

\opening{Dear Members of the  Admissions Committee,}

I am writing to strongly recommend Rasila Gautam for admission to the PhD program at the Australian National University. I have had the privilege of working with Ms. Gautam for the past two years, both as her academic supervisor for her Master's thesis and as a faculty member at College of Applied Sciences-Nepal, Tribhuvan University.

During her Master's research, Ms. Gautam demonstrated exceptional analytical skills and research aptitude while investigating the impacts of climate variability on agricultural productivity in Nepal's Banke district. Her work involved complex statistical analysis of climate data, extensive field surveys, and sophisticated modeling of climate-crop relationships. The resulting paper, which I co-authored with her, provides valuable insights into climate change adaptation strategies for Nepal's agricultural sector.

Ms. Gautam's academic performance has been consistently outstanding. She has shown remarkable ability to integrate diverse data sources, apply advanced statistical methods, and synthesize findings into clear, actionable recommendations. Her research on agricultural productivity showcases her capacity to conduct independent research while collaborating effectively with other researchers and local stakeholders.

Beyond her academic achievements, Ms. Gautam has proven herself to be an excellent communicator and team player. She presented her research findings at several departmental seminars, where her ability to explain complex concepts clearly and engage with audience questions impressed both faculty and peers. Her dedication to addressing real-world environmental challenges through rigorous scientific research makes her an ideal candidate for doctoral studies.

In conclusion, I am confident that Ms. Gautam will make significant contributions to your program and to the broader field of environmental science. Her combination of strong analytical skills, research experience, and genuine passion for understanding environmental challenges positions her perfectly for success in doctoral studies. Please feel free to contact me at hari.dahal@coas.tu.edu.np if you require any additional information.

\closing{Sincerely,}

\end{letter}

\end{document}