\documentclass[a4paper,11.5pt]{article}
\usepackage[left=0.6in, right=0.3in, top=0.4in, bottom=0.3in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{url}



\setlist[itemize]{noitemsep, topsep=0pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Rasila Gautam}}\\
    Kathmandu, Nepal\\
    Phone: +977 9868125455\\
    Email: \href{mailto:rasilagautam2@gmail.com}{rasilagautam2@gmail.com}\\
    LinkedIn: \url{https://www.linkedin.com/in/rasilagautam123/}
\end{center}

I am a dedicated Environmental Science graduate with comprehensive research experience in environmental and agricultural sciences, climate change, hydrological modeling, and geological assessments. My expertise includes research design, data analysis, and technical reporting.

\section{Education}

\begin{itemize}
    \item \textbf{MSc. Environmental Science} \hspace*{\fill} 2024\\
    College of Applied Sciences-Nepal, Tribhuvan University, Kathmandu, Nepal
    \item \textbf{BSc. Environmental Science} \hspace*{\fill} 2018\\
    Tri-Chandra Multiple Campus, Tribhuvan University, Nepal
    \item \textbf{Higher Secondary Education} \hspace*{\fill} 2014\\
    Adarsha Higher Secondary School, Nepalgunj, Banke, Nepal
    \item \textbf{Secondary Education} \hspace*{\fill} 2012\\
    Adarsha Higher Secondary School, Nepalgunj, Banke, Nepal

\end{itemize}


\section{Research and Fieldwork Experience}
\begin{enumerate}
    \item Research Paper (Published in \href{https://oaskpublishers.com/journal-of-environmental-science-and-agricultural-research-jesar-home}{Journal of Environmental Science and Agricultural Research (ISSN: 3029--0724)}): \href{https://oaskpublishers.com/assets/article-pdf/impact-of-climate-variability-on-agricultural-productivity-and-food-security--in-banke-nepal-insights-from-1990-2020.pdf}{Impact of Climate Variability on Agricultural Productivity and Food Security in Banke, Nepal: Insights from 1990--2020.}
    \item Research Paper (In Progress): \textit{Assessing Soil Nutrient Dynamics and Their Impacts on Crop Yields: A Case Study of Janaki Rural Municipality, Banke, Nepal}.
    \item Masters’ thesis: \textit{Impact of Climatic Variables on Crop Production and the Role of Environmental Factors in Janaki Rural Municipality, Banke, Nepal}.
    \item Bachelor's thesis: \textit{Assessment of Water Quality of Bagmati River by the Application of Canadian Water Quality Index along Kathmandu Valley}.
    \item Determined flood frequency analysis using Gumbel’s Distribution Method by application of HEC-HMS.
    \item Determined return period and create river channel geometry of Balkhu River Basin using HEC-RAS.
    \item Simulated the rainfall data of Surkhet Weather Station with the application of Statistical Downscaling Modelling (SDSM).
    \item Studied land-use change analysis of Balkhu.
    \item Conducted and evaluated a community based Solid Waste Management and Disaster Risk Management at ground level- Bansbari Secondary School Budhanilkahnta Municipality, Kathmandu
    \item Conducted a study on Disaster Risk Management of Barhabise Tatopani area of Sindhupalchok District, Nepal.
    \item Assessment of Processed ICE drinking water of JMC factory
    of Nepalgunj, Banke, Nepal.
    \item Assessment and Quantification POP-PBDEs (commercial pentaBDE) in Transportation sector in Nepal.
    \item Studied rock mass classification using rock mass rating, slope stability analysis through the  stereographic projection method, and paleo-channel of the river at Malekhu, as well as prepared an environmental geological map for Siddha-lake Rural Municipality, Dhading district.
    \item Conducted landslide assessment of upstream side of Malekhu Khola.
    \item Studied methods in ecological research, including light trapping and drift net techniques, assessed biodiversity along the roadside at Sarankot, and examined succession and fluvial deposits around Harpan Khola at Pame and Bhakunde.
    \item Studied Solid Waste Management Practice in Pokhara Municipal Sanitary Landfill Site.
    \item Assessed the heavy metals emission load for major type of Vehicles in Nepal.
    \item Measured and compared of noise level (equivalent, percentile) in residential, public and workplaces.
    \item Assessed water quality of surface and tap water.
 
\end{enumerate}

\section{Technical Skills}
\begin{itemize}
    \item Programming Languages: R (Basic), Python (Basic), Latex
    \item Software: SPSS, ArcGIS, HEC-HMS, HEC-RAS, SDSM, Cropwat
    \item Data Analysis: Quantitative and qualitative interpretation, climate and hydrological modeling
    \item Office Tools: Microsoft Office, Google Suite
    \item Fieldwork: Soil sampling, water quality assessment, biodiversity assessment, and environmental impact assessments, public consultations
    \item Research Skills: Literature review, survey design, data collection, and analysis, report writing
    \item Communication: Excellent written and verbal communication skills in English and Nepali
\end{itemize}

\section{Languages}
\begin{multicols}{3}
\begin{itemize}
    \item Nepali (Native)
    \item English (Fluent)
    \item Hindi (Conversational)
\end{itemize}
\end{multicols}

\section{Leadership and Volunteering}

\begin{itemize}
    \item \textbf{Action Learner, Volunteer Service Overseas/International Citizens Service (VSO/ICS), Sanepa, Lalitpur, Nepal} (17 July 2018--2 Oct 2018)

    \textbf{Duty Station:} Changuarayan-8, Bhaktapur, Nepal\\
    \textbf{Projects:} Empowerment of communities through awareness, training, peer learning, resource utilization, and united action
    \begin{itemize}
        \item Gender and Inclusive Governance Program
        \item PRAGATI: \textit{“Promoting resilient and sustainable urban growth by augmenting Disaster Risk
        Management (DRM) capacity of local authorities.”}
    \end{itemize}
    \item \textbf{Member, Leo Club of Kathmandu Sauharda} (2021--Present)
    \item \textbf{Board Member, Leo Club of Kathmandu Sauharda} (2020--2021)
    \item \textbf{Board Member, Leo Club of Kathmandu Dreams} (2017--2020)
    
    Dedicated to advancing social and environmental causes, I have actively participated in numerous events and programs aimed at development and awareness, led initiatives focused on heritage cleaning and community engagement, volunteered as a host and Master of Ceremonies for various programs, contributed to fundraising and disaster response efforts, supported club-organized activities such as heritage cleaning and trainings, and enhanced my leadership skills through participation in the Leo Leadership Training organized by the Lion Club.

\end{itemize}

\section{Trainings and Certifications}
\begin{itemize}
    \item Chemical Management with an Exercise on MSDS, April (14--28), 2022
    \item Global Climate Summit, Eco-Network, 2021
    \item GIS Training (11th November to 11th December, 2020)
    \item Environmental Impact Assessment Training (01st August -- 30th August, 2020)
    \item Community-Based Emergency Response Training by VSO and Nepal Red-Cross Society (2019)
    \item Leo Leadership Training (04th November 2017) by International Association of Lions Club
    \item Concise Vermicomposting Training (CVT) organized by Nepal Science Foundation Trust (NSFT) (2016)
    \item Fund Raising \textit{"The Great Centurian"} for community school (August 2016-- November 2016)
\end{itemize}










\section{Work Experience}

\begin{itemize}

    \item \textbf{Golden Group of Constructions Pvt. Ltd.} \hfill \textit{Hybrid / Remote} \\
    \underline{\textit{Environmental Associate }} \hfill \textbf{Feb 2025--Present} \\

        I assist in preparation of various environmental reports including EIA, IEE, BES, as well as monitoring reports. I analyze and evaluate field data, ensure compliance with environmental regulations, and support communication and public relations.
  
    \underline{\textit{Remote, Intern}} \hfill \textbf{Aug 2024--Feb 2025} \\
    
        Assisted in preparing EIA, IEE, BES reports and conducted environmental monitoring for various projects.

    \item
    \textbf{Pride Abroad Studies Pvt. Ltd.} \hfill \textit{On-site} \\
    \underline{\textit{Student Visa Counselor and GTE Officer}} \hfill \textbf{Jan 2021--Present} \\

    Assisting clients with comprehensive documentation for visa applications to Canada, Australia, the USA, the United Kingdom, Ireland, South Korea, and other countries.\\

    \underline{\textit{Counselor / Documentation Officer}} \hfill \textbf{Jan 2019--Dec 2020} \\

    Assisting clients with comprehensive documentation for visa applications to Canada, Australia, the USA, the United Kingdom, Ireland, South Korea, and other countries.

    \item
    \textbf{Volunteer Service Overseas (VSO ICS)} \hfill \textit{Kathmandu, Nepal} \\
    \underline{\textit{Action Learner (Intern)}} \hfill \textbf{Jul 2018--Oct 2018} \\
    Engaged in awareness raising, training sessions, peer education, infrastructure development, and community mobilization under gender and governance-focused development programs.

\end{itemize}















\section{References}
\begin{multicols}{2}
\textbf{Academic References}\\
\begin{itemize}
    \item Dr. Bhupendra Devkota, Principal, College of Applied Sciences-Nepal\\
    Email: \href{mailto:bhupendra.devkota@gmail.com}{bhupendra.devkota@gmail.com}\\

    \item Dr. Hari Dahal, Professor, College of Applied Sciences-Nepal\\
    Email: \href{mailto:dahaldr.hari@gmail.com}{dahaldr.hari@gmail.com}\\

    \item Dr. Tirtha Raj Adhikari, Professor, College of Applied Sciences-Nepal\\
    Email: \href{mailto:tirtha43@gmail.com}{tirtha43@gmail.com}
\end{itemize}
\columnbreak

\textbf{Work References}\\
\begin{itemize}
    \item Ms. Mala Pradhan, Project Coordinator of Placement Changunarayan (2018/2019), Volunteer Service Overseas\\
    Email: \href{mailto:mala.pradhan92@gmail.com}{mala.pradhan92@gmail.com}\\

    \item Mr. Krishna Dulal, Managing Director, Pride Abroad Studies Pvt. Ltd.\\
    Email: \href{mailto:krishna@pride.edu.np}{krishna@pride.edu.np}
\end{itemize}
\end{multicols}

\vspace{1cm}
\textbf{Declaration:} I hereby declare that the information provided above is true and correct to the best of my knowledge.




\textbf{Rasila Gautam}\\

\end{document}
