\section{Education System of USA}
The education system in the United States is highly decentralized and diverse, with each state managing its own public education system meaning that there isn't a single national curriculum or governing body that dictates educational standards across the entire country but control over education largely rests with individual states and local school districts which leads to significant variation in curriculum, funding, and policies from one states to another.
The typical structure and key aspects of the U.S. education system:

\textbf{I. Levels of Education}

\begin{enumerate}
    \item \textbf{Early Childhood Education (Ages 3--5):}
    \begin{itemize}
        \item Preschool / Pre-kindergarten
        \item Kindergarten
    \end{itemize}

    \item \textbf{Primary/Elementary Education:} Grades K--5 or K--6 (approximately ages 5--11)

    \item \textbf{Middle School / Junior High School:} Grades 6--8 or 7--8 (approximately ages 11--14)

    \item \textbf{Secondary / High School:} Grades 9--12 (approximately ages 14--18)

    \item \textbf{Post-Secondary / Higher Education (Ages 18+):}
    \begin{itemize}
        \item \textbf{Community Colleges (2-year institutions):}
        \begin{itemize}
            \item Offer associate degrees (e.g., Associate of Arts (AA), Associate of Science (AS)) and vocational certificates.
            \item Many students transfer to a four-year university after completing an associate degree.
        \end{itemize}

        \item \textbf{Colleges and Universities (4-year institutions):}
        \begin{itemize}
            \item \textbf{Undergraduate Degrees (Bachelor's):}
            \begin{itemize}
                \item Typically takes 3--4 years.
                \item Common degrees include Bachelor of Arts (BA) and Bachelor of Science (BS).
            \end{itemize}

            \item \textbf{Graduate Degrees:}
            \begin{itemize}
                \item \textbf{Master's Degree:} 1--3 years of specialized study after a bachelor's (e.g., MA, MS, MBA).
                \item \textbf{Doctoral Degree:} The highest academic level, requiring research and a dissertation (Ph.D., Ed.D., M.D., J.D. — typically 3--7+ years).
            \end{itemize}
        \end{itemize}
    \end{itemize}
\end{enumerate}

\textbf{II. Key Characteristics of the US Education System}
US education system is known for its flexibility, diversity, and emphasis on experiential learning. Some key characteristics include:
\begin{itemize}
    \item \textbf{Decentralization:} Education is primarily managed at the state and local levels, leading to significant variations in curriculum, funding, and policies.
    \item \textbf{Diverse Curriculum:} Schools offer a wide range of subjects, including core subjects (math, science, language arts, social studies) and electives (arts, music, physical education).
    \item \textbf{Standardized Testing:} Standardized tests (e.g., SAT, ACT) are often used for college admissions and assessing student performance.
    \item \textbf{Extracurricular Activities:} Schools encourage participation in sports, clubs, and other extracurricular activities to promote holistic development.
    \item \textbf{Higher Education Opportunities:} The U.S. has a vast network of colleges and universities offering diverse programs and degrees.
    \item \textbf{Student-Centered Learning:} Emphasis on critical thinking, problem-solving, and experiential learning through projects, internships, and community service.
\end{itemize}

\textbf{National Qualifications Framework}

The United States does not currently have a formal National Qualifications Framework (NQF). However, efforts are underway to establish a United States Qualifications Framework (USQF) to enhance the recognition, mobility, and interoperability of educational qualifications.
US educational system is diverse and offers a wide range of institutions at different levels and major are as follows: -
\begin{itemize}
    \item K-12 Education (Primary and Secondary)
    K-12 refers to schooling from Kindergarten to 12th grade. It is the foundational education system before higher education. Public schools, Private schools and Homeschooling are the institution for k-12 education.
    \item Higher Education (Post-Secondary)
    The US higher education includes about 4,500 institutions. These institutions offer a variety of programs and degrees, from associates to doctoral. Institutions involved for higher education are Public Universities, Private universities, Ivy League Universities, Community Colleges, Liberal Arts Colleges, Technical Colleges (or Vocational/Trade Schools), Research Universities and Other Specialized Institutions.
\end{itemize}


The United States education system offers a variety of educational programs across various fields, making it a top destination for international students. Some of them are as follows:

\begin{enumerate}
    \item Computer Science \& Information Technology
    \item Business Administration (MBA \& Finance)
    \item Engineering
    \item Healthcare \& Medicine
    \item Data Science \& Artificial Intelligence
    \item Law
    \item Psychology \& Social Sciences
    \item Arts \& Design
    \item Environmental Science \& Sustainability
    \item Media \& Communication Studies
\end{enumerate}

\textbf{Tuition Fees Overview}
Tuition fees in the United States vary widely based on factors such as the type of institution (public vs. private), level of study (undergraduate vs. graduate), and the specific program or major. On average, tuition fees for international students can range from \$20,000 to \$60,000 per year for undergraduate programs and \$30,000 to \$70,000 per year for graduate programs.
\begin{table}[h!]
\centering
\begin{tabular}{|l|c|c|}
\hline
\textbf{Course Category} & \textbf{Bachelor's Degree (Annual)} & \textbf{Master's Degree (Annual)} \\
\hline
Engineering & \$25,000--\$50,000 & \$30,000--\$60,000 \\
Business Administration & \$30,000--\$60,000 & \$30,000--\$70,000 \\
Computer Science & \$25,000--\$50,000 & \$30,000--\$60,000 \\
Healthcare/Medicine & \$30,000--\$60,000 & \$35,000--\$70,000 \\
Social Sciences & \$20,000--\$45,000 & \$25,000--\$50,000 \\
Fine Arts/Design & \$30,000--\$60,000 & \$35,000--\$70,000 \\
Environmental Science & \$25,000--\$50,000 & \$30,000--\$60,000 \\
Psychology & \$20,000--\$45,000 & \$25,000--\$50,000 \\
Education & \$20,000--\$45,000 & \$25,000--\$50,000 \\
Communication/Media & \$25,000--\$50,000 & \$30,000--\$60,000 \\
\hline
\end{tabular}
\caption{Estimated Annual Tuition Fees for Major Fields of Study in the USA}
\end{table}

\textit{Note: Tuition fees can vary based on the institution and program specifics.}

\subsection{Scholarships and Financial Aid}
The United States offers a wide range of scholarships and financial aid options for both domestic and international students. These can significantly reduce the cost of education. Here are the major scholarship categories and opportunities:

\subsubsection{U.S. Government Scholarships}
\begin{itemize}
    \item \textbf{Fulbright Program (Master's/PhD):}
    \begin{itemize}
        \item Covers full tuition, airfare, living expenses, and health insurance
        \item 2026-27 application deadline: April 30, 2025
        \item Check USEF Nepal for future updates
        \item Requirements: Strong academic record and leadership experience
    \end{itemize}

    \item \textbf{Hubert H. Humphrey Fellowship:}
    \begin{itemize}
        \item Designed for mid-career professionals
        \item Focus on leadership in fields like public health
        \item 2025-26 applications closed; monitor USEF Nepal for future opportunities
    \end{itemize}
\end{itemize}

\subsubsection{University Scholarships}
\begin{itemize}
    \item \textbf{Full-Ride Scholarships:}
    Most of the universities in the USA offer full-ride scholarships to international students, which cover tuition, living expenses, and sometimes even travel costs. Some notable examples include:
    \begin{itemize}
        \item Harvard: Free tuition for families earning \$75,000/year
        \item Details available on respective university websites
    \end{itemize}

    \item \textbf{Partial Scholarships:}
    Many universities offer partial scholarships that cover a portion of tuition fees. Examples include:
    \begin{itemize}
        \item University of Oregon ICSP Scholarship: \$7,500--\$30,000/year
        \item University of Minnesota Global Excellence Scholarship: \$10,000/year
        \item Search university websites for "international student scholarships"
    \end{itemize}
\end{itemize}

\subsubsection{Private Scholarships}
Private scholarships are offered by various organizations, foundations, and corporations. They can be merit-based, need-based, or specific to certain fields of study. Some notable private scholarship programs include:
\begin{itemize}
    \item \textbf{Gates Millennium Scholars Program:}
    \begin{itemize}
        \item For outstanding minority students
        \item Covers tuition, fees, and living expenses
        \item Application deadline: January 15, 2025
    \end{itemize}

    \item \textbf{Jack Kent Cooke Foundation Scholarships:}
    \begin{itemize}
        \item For high-achieving students with financial need
        \item Covers up to \$40,000/year for undergraduate studies
        \item Application deadline: November 1, 2024
    \end{itemize}

    \item \textbf{College Board Scholarship Search:}
    \begin{itemize}
        \item Online tool to find scholarships based on various criteria
        \item Free to use; no registration required
    \end{itemize}
\end{itemize}

\subsubsection{Nepal Government Scholarships}
Limited opportunities for U.S. studies; periodically check with the Ministry of Education, Science and Technology (MOEST) for updates.

\subsubsection{Working While Studying}
International students in the U.S. can work part-time while studying, which can help cover living expenses and provide valuable experience. Here are the main options:
\begin{itemize}
    \item \textbf{On-Campus Employment:}
    \begin{itemize}
        \item Allowed for F-1 visa holders
        \item Up to 20 hours per week during the academic year
        \item Full-time during holidays and breaks
    \end{itemize}

    \item \textbf{Curricular Practical Training (CPT):}
    \begin{itemize}
        \item Paid internships or co-op programs related to the field of study
        \item Must be authorized by the Designated School Official (DSO)
    \end{itemize}

    \item \textbf{Optional Practical Training (OPT):}
    \begin{itemize}
        \item Work authorization for up to 12 months after graduation
        \item STEM graduates can apply for a 24-month extension
        \item Requires application to U.S. Citizenship
    \end{itemize}
\end{itemize}    

\subsubsection{Tips for Scholarship Success}
\begin{itemize}
    \item Start early: Most deadlines are 6-12 months before study begins
    \item Craft compelling essays that highlight contributions to Nepal
    \item Use official resources to avoid scams:
    \begin{itemize}
        \item EducationUSA Nepal
        \item USEF Nepal
    \end{itemize}
    \item Seek free counseling from EducationUSA Nepal and USEF Nepal
\end{itemize}

\subsection{Accreditation of Institutions}

In the United States, higher education institutions are accredited by both institutional and programmatic accrediting bodies. These organizations are recognized by the U.S. Department of Education and the Council for Higher Education Accreditation (CHEA). Regional accrediting bodies focus on institutions within specific geographical areas, while specialized agencies evaluate particular programs or types of institutions. 
Regional Accrediting Bodies:

\begin{itemize}
    \item Higher Learning Commission (HLC): The Higher Learning Commission accredits institutions in a large geographic region, including many states in the Midwest and surrounding areas.
    \item Middle States Commission on Higher Education (MSCHE): MSCHE accredits institutions in the Mid-Atlantic region, including states like Pennsylvania, New Jersey, Delaware, Maryland, and others. 
    \item New England Commission of Higher Education (NECHE): NECHE accredits institutions in the New England states. 
    \item Southern Association of Colleges and Schools Commission on Colleges (SACSCOC): SACSCOC accredits institutions in the Southern states.
    \item Northwest Commission on Colleges and Universities (NWCCU): NWCCU accredits institutions in the Northwest.
    \item Western Association of Schools and Colleges Senior College and University Commission (WSCUC): WSCUC accredits institutions in the Western region. 
    \item Accrediting Commission for Career Schools and Colleges (ACCSC): The Accrediting Commission for Career Schools and Colleges (ACCSC) accredits career and technical schools, as well as some vocational and higher education institutions. 
    \item Accreditation Council for Business Schools and Programs (ACBSP): ACBSP accredits business programs at institutions of higher education.
    \item Commission on Collegiate Nursing Education (CCNE): CCNE accredits nursing programs, ensuring they meet rigorous standards. 
    \item Council on Occupational Education (COE): COE accredits institutions offering vocational education and training programs. 
    \item Distance Education Accrediting Commission (DEAC): DEAC accredits distance education programs.
    \item ABET (Accrediting Board for Engineering and Technology): ABET accredits engineering, technology, and computing programs. 
    \item National Architectural Accrediting Board (NAAB): NAAB accredits professional degree programs in architecture.
    \item Council on Education for Public Health (CEPH): CEPH accredits schools of public health and public health programs. 
\end{itemize}

\subsubsection{Importance of verifying institutional legitimacy}
It is crucial for students, especially international applicants, to verify the accreditation status of any institution or program before enrolling. Attending an accredited institution ensures that the education received meets recognized quality standards, which is important for the recognition of degrees by employers, professional licensing boards, and other educational institutions. Unaccredited institutions may not provide valid qualifications, and credits earned may not be transferable. Therefore, prospective students should consult official resources, such as the U.S. Department of Education or the Council for Higher Education Accreditation (CHEA), to confirm the legitimacy of an institution or program.


