\section{Introduction}

\subsection{Background}

The United States of America(USA) also known as power house of world. The United States of America (USA) is located in North America. This country is situated in Northern and Western Hemispheres. It is located in Latitude: 24° to 49° N and Longitude: 66° to 125° W. It shares border with Canada in North, Mexico in South, Atlantic Ocean in East, Pacific Ocean in West.  Additional Territories of USA also includes Alaska (northwest of Canada), Hawaii (an island state in the central Pacific Ocean), Territories such as Puerto Rico, Guam, U.S. Virgin Islands, American Samoa, and Northern Mariana Islands. The U.S.A has access to both the Atlantic and Pacific Oceans, contributing to its historical and current role as a major global power in trade, politics, and military influence.

The history of the United States includes centuries of indigenous cultures, colonization, revolution, expansion, conflict, and global influence. In 1492 Christopher Columbus' team initiated European exploration. 13 British colonies were established along the East Coast. Tensions with Native Americans grew; indigenous populations declined due to disease and conflict. In the course of time conflict arose over British taxes and governance without representation. In 1776 declaration of independence authored by Thomas Jefferson and then in 1783 victory in the Revolutionary War and recognition of U.S. independence in the Treaty of Paris. In 1787 U.S. Constitution adopted, creating a federal republic and in 1789 George Washington became the first president.

The United States has a dynamic and diverse demography due to various factors like birth rates, death rates, and immigration. Major key aspects of USA’s demography include the following:



\begin{enumerate}
    \item \textbf{Population Size and Composition}
    \begin{itemize}
        \item The U.S. is the third most populated country globally, with an estimated population of 340.1 million as of July 1, 2024.
        \item The population grew by approximately 2.6\% from the 2020 census (331.4 million).
        \item The annual growth rate in 2024 was around 1\%, which is slightly below the global average.
        \item Life Expectancy (2023): 78.4 years overall; 75.8 years for males and 81.1 years for females.
        \item Urban Population: Approximately 82.4\% of the population resides in urban areas.
        \item Immigration has become the primary source of population growth since 2021, reflecting significant demographic shifts in age, race, and ethnicity.
        \item Without immigration, projections show the U.S. population would begin to shrink by 2033.
        \item Foreign-born residents reached 14.3\% in 2023, the highest since 1910, driven largely by Latin American migration.
    \end{itemize}

    \item \textbf{Age Structure}
    \begin{itemize}
        \item Under 18 years: 21.7\%
        \item 18--44 years: 36.0\%
        \item 45--64 years: 24.6\%
        \item 65 and over: 17.7\%
        \item The U.S. population is steadily aging.
        \item The 65+ group was the fastest-growing between 2010 and 2022, increasing by 42.8\%.
        \item By 2100, 29.1\% of Americans will be 65 or older, while only 16.4\% will be under 18. The median age is projected to rise to 47.9 years from 38.9 in 2022.
    \end{itemize}

    \item \textbf{Race and Ethnic Composition}
    \begin{itemize}
        \item White alone: 75.3\% (58.4\% White alone, not Hispanic or Latino)
        \item Black alone: 13.7\%
        \item Asian alone: 6.4\%
        \item American Indian and Alaska Native alone: 1.3\%
        \item Native Hawaiian and Other Pacific Islander alone: 0.3\%
        \item Two or More Races: 3.1\%
        \item Hispanic or Latino (any race): 19.5\%
        \item By 2050, the non-Hispanic White population is expected to fall below 50\%.
    \end{itemize}

    \item \textbf{Fertility and Mortality}
    \begin{itemize}
        \item Fertility rate (2023--2024): 1.78--1.79 births per woman.
        \item This is below the replacement level of 2.1 births per woman.
        \item Birth rates are declining due to delayed marriage and shifting demographics.
    \end{itemize}

    \item \textbf{Mortality Rates}
    \begin{itemize}
        \item Crude death rate: 8.7 per 1,000 population (2023)
        \item Leading causes: Heart disease, cancer, unintentional injuries
        \item COVID-19 dropped from 4th in 2022 to 10th in 2023
        \item Infant mortality rate: 5.4 per 1,000 live births
        \item Deaths projected to exceed births annually by 2038
    \end{itemize}

    \item \textbf{Immigration}
    \begin{itemize}
        \item 47.8 million foreign-born residents in 2023 (14.3\% of population) — highest since 1910.
        \item Largest annual increase in immigrant population in 20+ years.
        \item Major source countries: Mexico, India, China, Philippines, several African nations, El Salvador.
        \item Immigrants significantly contribute to labor markets in healthcare, agriculture, and construction.
        \item 77\% are legal residents; 23\% are unauthorized.
    \end{itemize}
\end{enumerate}



In summary, the demography of the USA is characterized by a growing but aging population, increasing racial and ethnic diversity driven by immigration, and declining fertility rates that are leading to an eventual natural decrease in population without the continued influx of immigrants.

The United States consist of many large and influential cities, having economic, cultural, and political diversity. The following are consistently among the largest and most significant cities by population:

\subsection{Major Cities of USA}
The United States is home to many large and influential cities, each contributing to the country's economic, cultural, and political diversity. The following are consistently among the largest and most significant cities by population:

\begin{enumerate}
    \item \textbf{New York City, New York:} The most populated city in the U.S. and a global center for finance, media, fashion, art, and culture. Its metropolitan area is one of the largest in the world with an estimated population of 8.34 million.
    \item \textbf{Los Angeles, California:} The second largest city in the USA, known for its entertainment industry (Hollywood), diverse economy, and cultural institutions. Estimated population: 3.82 million.
    \item \textbf{Chicago, Illinois:} A major hub in the Midwest, known for its architecture, arts scene, and as a transportation and business center. Estimated population: 2.67 million.
    \item \textbf{Houston, Texas:} A rapidly growing city, known for its energy industry, NASA's Johnson Space Center, and diverse population. Estimated population: 2.3 million.
    \item \textbf{Phoenix, Arizona:} One of the fastest-growing major cities in the U.S., experiencing significant population growth in the Sun Belt region. Estimated population: 1.64 million.
    \item \textbf{Philadelphia, Pennsylvania:} A historically rich city, a major East Coast hub, and an important economic and cultural center. Estimated population: 1.57 million.
    \item \textbf{San Antonio, Texas:} A city with a strong historical and cultural identity, known for the Alamo and its rapidly growing population. Estimated population: 1.47 million.
    \item \textbf{San Diego, California:} A major coastal city with a strong military presence, a thriving tourism industry, and a pleasant climate. Estimated population: 1.38 million.
    \item \textbf{Dallas, Texas:} Another rapidly growing Texas city, a major business and cultural center in the DFW metropolis. Estimated population: 1.3 million.
    \item \textbf{Jacksonville, Florida:} The most populous city in Florida by land area, a growing port city with a diverse economy. Estimated population: 1.1 million.
\end{enumerate}

Other major U.S. cities include Austin (Texas), Fort Worth (Texas), San Jose (California), Columbus (Ohio), Charlotte (North Carolina), Indianapolis (Indiana), San Francisco (California), Seattle (Washington), Denver (Colorado), Oklahoma City (Oklahoma), Nashville (Tennessee), Washington, D.C., Boston (Massachusetts), Las Vegas (Nevada), Detroit (Michigan), Portland (Oregon), Memphis (Tennessee), Baltimore (Maryland), Milwaukee (Wisconsin), Atlanta (Georgia), and Miami (Florida).

\subsection{Economy of USA}
The United States has the largest economy in the world, characterized by a mixed economic system that combines elements of capitalism and government intervention. The U.S. economy is highly developed, technologically advanced, and diverse, with significant contributions from various sectors including services, manufacturing, agriculture, and technology.

As of May 2025, the U.S. economy is exhibiting signs of slowing growth, influenced by policy shifts, global trade tensions, and evolving consumer behavior. The U.S. economy is the world's largest economy, characterized by a diverse, highly developed, and private-sector-led structure. It comprises of high levels of productivity, technological innovation, and competitiveness, along with a flexible labor market and the advantage of the U.S. dollar as the world's reserve currency.
As per Q4 2024 reports real GDP increased by 2.4\% annually and Q1 2025 reports shows real GDP decreased by 0.3\% annually due to an increase in imports and a decrease in government spending. Expected GDP growth of 2024 is 2.8\% annually and forecasted GDP growth of 2025 is 1.8\%. April 2025: The annual inflation rates up to April 2025 (Consumer Price Index - CPI) is 2.3\%, which is the lowest since February 2021. Core Inflation (excluding food and energy): 2.8\% in April 2025. The unemployment rate was 4.2\% in April 2025 and the number of unemployed people in April 2025 was 7.2 million. Monthly job additions are expected to average between 80,000 and 100,000 in 2025, a decrease from 200,000 earlier in the year. The U.S. monthly international trade deficit increased in March 2025 to \$140.5 billion, as imports increased more than exports. The U.S. fiscal deficit averaged 5.9\% of GDP in the decade leading up to 2024. The U.S. economy in May 2025 is characterized by slowing growth, a cooling labor market, and rising inflation. With the formation of New Government under the leadership of Donald Trump, policy decisions, including trade tariffs and fiscal measures, are contributing to economic uncertainties. 







